Contributions

### 2023-08-28 ADMIN_02_contributions.Rmd
couple minor edits to contributors list

# Active Contributors 
#### [Katherine Silliman, PhD](https://ksilliman.weebly.com/), NOAA Atlantic Oceanographic and Meteorological Lab - katherine.silliman[at]noaa.gov (Working Group Co-leader) {.unlisted .unnumbered}
#### [Sam Bogan](http://www.hofmannlab.com/sam-bogan.html), UC-Santa Barbara -snbogan[at]ucsb.edu {.unlisted .unnumbered}
#### Tait Algayer, Washington State University {.unlisted .unnumbered}
#### Len Aguila, Texas A&M University Galveston {.unlisted .unnumbered}
#### [Danielle Davenport, PhD](https://www.researchgate.net/profile/Danielle-Davenport-2), Fisheries and Oceans Canada {.unlisted .unnumbered}  
#### Stephen Gaughran, PhD, Princeton University {.unlisted .unnumbered}
#### Thea Gessler, Iowa State University {.unlisted .unnumbered}
#### [Joanna Griffiths, PhD](https://joannasgriffiths.wordpress.com/), UC-Davis {.unlisted .unnumbered}
#### Jason Johns, UC-Santa Barbara (Website Manager) {.unlisted .unnumbered}
#### Sarit Truskey, Northeastern University {.unlisted .unnumbered}

>>>>

# Active Contributors 
#### [Katherine Silliman, PhD](https://ksilliman.weebly.com/), NOAA Atlantic Oceanographic and Meteorological Lab - katherine.silliman[at]noaa.gov (Working Group Co-leader) {.unlisted .unnumbered}
#### [Sam Bogan](http://www.hofmannlab.com/sam-bogan.html), UC-Santa Barbara - snbogan[at]ucsb.edu (Working Group Co-leader) {.unlisted .unnumbered}
#### Tait Algayer, Washington State University {.unlisted .unnumbered}
#### Len Aguila, Texas A&M University Galveston {.unlisted .unnumbered}
#### [Danielle Davenport, PhD](https://www.researchgate.net/profile/Danielle-Davenport-2), Fisheries and Oceans Canada {.unlisted .unnumbered}  
#### Stephen Gaughran, PhD, Princeton University {.unlisted .unnumbered}
#### Thea Gessler, Iowa State University {.unlisted .unnumbered}
#### [Joanna Griffiths, PhD](https://joannasgriffiths.wordpress.com/), UC-Davis {.unlisted .unnumbered}
#### Jason Johns, UC-Santa Barbara - jasonjohns[at]ucsb.edu (Website Manager) {.unlisted .unnumbered}
#### Sarit Truskey, Northeastern University {.unlisted .unnumbered}
